Investigation on GIT

### 2010-04-25 paper.tex
add fetch/pull

Estos dos conceptos son distintos al check in / check out centralizado, 
consisten en el envío o recepción de commits entre dos repositorios. Aquí 
explicaremos un poco en que consisten y cuando hay que usar uno u otro.

>>>>

When we want to share our work with the rest of the team we have two basic concepts, Push & Pull
Push refers to taking all my changes and add them to the repository of another co-worker
Pull is a compose action of fetch + merge, where fetch takes the changes from selected repository of a co-worker and copy them to my local repository, merge obiously merges those changes with the sourcecode of my local repository
At the same way, another co-worker can do Pull over my repo and get my new code & changes

%Estos dos conceptos son distintos al check in / check out centralizado, 
%consisten en el envío o recepción de commits entre dos repositorios. Aquí 
%explicaremos un poco en que consisten y cuando hay que usar uno u otro.
